A Classical Density-Functional Theory for Describing Water Interfaces

### 2011-08-14 paper/project.tex
Some intro text added to project.tex

>>>>

The simple yet complex water molecule is one of the most important 
substances for life and industry. The structure and geometry of the 
water molecule leads to a strong polarity and complex intermolecular
forces. The hydrogen bonds formed by water are very strong, creating
tetragonal clusters (CITE?) that lead to many of water's unusual properties,
such as the comparatively high melting, boiling, and critical temperatures.
The large dielectric constant (D~80) (CITE) is partially responsible for
water as a universal solvent, along with the ease of availability and use.

It is challenging to describe all the relevant properties of water using
a model, especially if a low computational cost is also desired.

(Previous/popular models of water summary/review??)
